The \dealii{} Library, Version 9.4

### 2022-05-25 9.4/paper.tex
Leave a note.

The setup process is visualized in Figure~\ref{fig:repartitioning}. At first, cells, incl. their
surrounding (ghost) cells and parent cells, are collected and 
sent to the new owner. On the
receiving side, the sets of all cells are combined and possible duplicates
are removed. This information is enough to construct a new triangulation.
For sending/receiving, we apply consensus-based algorithms~\cite{hoefler2010scalable}, which
we introduced into the library in release 9.2~\cite{dealII92}. Consensus-based 
algorithms are used also in \cite{ibanez2016pumi} for repartitioning.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Topic 6}

>>>>

The setup process is visualized in Figure~\ref{fig:repartitioning}. At first, cells, incl. their
surrounding (ghost) cells and parent cells, are collected and 
sent to the new owner. On the
receiving side, the sets of all cells are combined and possible duplicates
are removed. This information is enough to construct a new triangulation.
For sending/receiving, we apply consensus-based algorithms~\cite{hoefler2010scalable}, which
we introduced into the library in release 9.2~\cite{dealII92} -- see
also Section~\ref{sec:CA}. Consensus-based
algorithms are used also in \cite{ibanez2016pumi} for repartitioning.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improvements to unstructured communication}
\label{sec:CA}

\todo[inline]{Wolfgang to write something about the CA algorithms (and to give
credit to the previous implementation by Peter).}

Also reference Section~\ref{sec:repartitioning}.
